---
title       : Data Products Project
subtitle    : BMI Test
author      : Nino White
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- .class #id 

## Health

There is an old saying, "at least I have my health", and that saying has never been more true than in today's age of fast meals and less active lifestyles!

--- .class #id

## BMI

The Body Mass Index, or BMI, is a calculation used to determine your level of body fat. It is a quick gauge of a persons overall fitness and risk of developing chronic diseases. 

--- .class #id

## What the Result Means

Generally, if you're at a healthy weight, your body mass index should fall between 18.5 and 24.9, notes the National Heart, Lung and Blood Institute. If your BMI is below 18.5, you could be underweight. On the other hand, a BMI greater than 25.0 is categorized as overweight, while a score above 30 is considered obese.

--- .class #id

## Average Female BMI by Size

```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
data(women)
women$BMI <- (women$weight*703)/(women$height^2)
local({r <- getOption("repos"); 
       r["CRAN"] <- "http://cran.r-project.org"; options(repos=r)})
install.packages("scatterplot3d")
library(scatterplot3d)
attach(women)
```

```{r warning=FALSE, message=FALSE}
scatterplot3d(height, weight, BMI, main = "Female  BMI", pch = "16", type = "h")
```

